Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
[D|T] -> \cite

All list terms for all variables are unordered.  The Pbcs form a
classical finite set-of-subsets lattice.  In addition, we have left
out a number of other annotations that are irrelevant for the basic
description of the annotator and straightforward to handle:
$Dictionary$, $Tuple$, $Float$, $UnicodePoint$, $Iterator$, etc.  The
complete list is described in [T].

@@

It is outside the scope of the present paper to describe the type
inference engine and the rules more formally.  The difficult points
involve mutable containers -- e.g.\ initially empty list that are filled
somewhere else -- and the discovery of instance attributes -- in Python,
classes do not declare upfront a fixed set of attributes for their
instances, let alone their types.  Both these examples require
sophisticated reflowing techniques that invalidate existing types in
already-annotated basic blocks, to account for the influence of more
general types coming indirectly from a possibly distant part of the
program.  The reader is referred to [D] for more information.

@@

We give formal termination and correctness proofs in [D], as well as
worst-case bounds and some experimental evidence of their practical
irrelevance.

>>>>

All list terms for all variables are unordered.  The Pbcs form a
classical finite set-of-subsets lattice.  In addition, we have left
out a number of other annotations that are irrelevant for the basic
description of the annotator and straightforward to handle:
$Dictionary$, $Tuple$, $Float$, $UnicodePoint$, $Iterator$, etc.  The
complete list is described in document \cite{T}.

@@

It is outside the scope of the present paper to describe the type
inference engine and the rules more formally.  The difficult points
involve mutable containers -- e.g.\ initially empty list that are
filled somewhere else -- and the discovery of instance attributes --
in Python, classes do not declare upfront a fixed set of attributes
for their instances, let alone their types.  Both these examples
require sophisticated reflowing techniques that invalidate existing
types in already-annotated basic blocks, to account for the influence
of more general types coming indirectly from a possibly distant part
of the program.  The reader is referred to technical report \cite{D}
for more information.

@@

We give formal termination and correctness proofs in \cite{D}, as well as
worst-case bounds and some experimental evidence of their practical
irrelevance.
